Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-11-17 manuscript/response_to_reviewer_comments.tex

\medskip
{\it 1.12. Lines 77-80: I think a stronger argument for why deep active-layer soils can be made, and it would be helpful to clarify what are the 'strong effects' of warming. }

Agreed. See our response to comment 1.8 above.

\medskip
{\it 1.13. I cannot tell if C:N, \%C and \%N were measured at the end of the incubation. Could these results be collated in a table in the manuscript? Otherwise the methods section appears to be detailed and well written. }

C and N were measured for all samples post-incubation, and in the 'extra' group (l. 128-129) pre-incubation. This will be clarified in the methods, particularly lines 162-, which we agree were ambiguous. A new Table 1 now summarizes a variety of physical and flux data by treatment. Reviewer 2 also raised the idea of looking at C/N, and we have responded to that suggestion in detail (see comment 2.9). {\bf See new lines TODO.}

@@

\medskip
{\it 1.14. Line 232: In this section it would also be interesting to know the soil respiration decay rate per treatment over the course of the incubation experiment. }

This has been included in the new Table 1 (see comment 1.13 above).

### 2016-11-17 manuscript/cpcrw_manuscript.Rmd
Added BD, caption, tweaks to Table 1

**Table 1.** New one.

```{r table1, echo=FALSE}
knitr::kable(table1)
```

>>>>

**Table 1.** Summary of dissolved organic carbon (DOC), percent C, percent N, and CO~2~ and CH~4~ fluxes by treatment (with pre-incubation values shown in the right-hand column). Each column summarizes (mean ± s.d.) a separate group of N=6 cores.

```{r table1, echo=FALSE}
knitr::kable(table1, align = "r")
```
